---
title       : Quick way to predict iris species 
subtitle    : Use machine learning to blow away your peers
author      : Li Jiang
job         : Coursera learner
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Why create this app

1. For botanist who want to study taxonomy 
2. For people who enjoy knowing about iris species 
3. For appreication of the power of machine learning 

--- .class #id

## Sizes of sepal and petal are useful parameters in predicting iris species

As shown by the plot with sepal and petal width below, 3 iris species represented with 3 different colors are clearly separated, with little overlap.

The size of sepal and petal are reliable parameters for predicting iris species 

```{r,echo=FALSE,fig.width=5,fig.height=5}
library(caret)
library(rattle)
library(rpart)
data(iris)
g<-ggplot(iris,aes(Petal.Width,Sepal.Width,colour=Species))
g+geom_point(size=4)+
  theme_classic()+
  ggtitle("Petal and sepal width")+
  xlab("Petal Width (cm)")+
  ylab("length (cm)")+
  theme(plot.title = element_text(size = rel(1.6)))+
  theme(axis.title = element_text(size = rel(1.25)))
  
```

--- .class #id

## Predict iris species by decision tree
```{r,echo=FALSE}
inTrain <- createDataPartition(y=iris$Species,p=0.7,list=FALSE)
training <- iris[inTrain,]
testing <- iris[-inTrain,]
modFit <- train(Species~., method="rpart",data=training)
fancyRpartPlot(modFit$finalModel)
```

--- .class #id

## Iris prediction by tree method is very accurate (accuracy=0.96) 

```{r,echo=FALSE}
pred <- predict(modFit,testing)
result <- confusionMatrix(pred,testing[ ,5])
result
```
